### 2016-07-08 intro.tex
no message

\jnote{Are we being too specific by focusing on hash-based
set-membership only? It would be nice to give general definitions
that apply to arbitrary data structures (constructed in arbitrary
ways) and then only later specialized to hash-based Bloom filters.}

>>>>

\jnote{Are we being too specific by focusing on hash-based
set-membership only? It would be nice to give general definitions
that apply to arbitrary data structures (constructed in arbitrary
ways) and then only later specialized to hash-based Bloom filters.
(Put this in an appendix for now, until we see how things play
out.)}
